\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}

%opening
\title{Autonomous Cars}
\author{Markus Reichl}

\begin{document}

\maketitle

\section{Introduction}
An autonomous car (driverless car, self-driving car, robotic car) is a vehicle that is capable of sensing its environment and navigating without human input.

Autonomous cars can detect surroundings using technologies such as radar, GPS and computer vision. 
Advanced control systems interpret sensory information to identify appropriate navigation paths, obstacles and also other cars.

\section{History}
Experiments have been conducted on automating cars since at least the 1920s. 
The first autonomous cars appeared in the 1980s. 
Since then, numerous major companies and research organisations have developed working prototype autonomous vehicles.
As of 2013, four U.S. states have passed laws permitting autonomous cars and cities in Europe allowed testing in traffic.

\section{Classification}
The Society of Automotive Engineers (SAE) defined 6 levels of automated vehicles:
\begin{itemize}
 \item Level 0: No vehicle control, but may issue warnings.
 \item Level 1: Vehicle assists the driver.
 \item Level 2: System controls accelerating and breaking.
 \item Level 3: Self-driving within known environments.
 \item Level 4: System controls the vehicle in most environments.
 \item Level 5: Other than setting the destination and starting the system, no human intervention is required.
\end{itemize}

\section{Waymo}
Above all the autonomous cars on the market, Google's self-driving car \textbf{Waymo} is probably the best known example.
Their first driver-less car was built in 2009 had a huge influence on the market and also created a lot of ethical questions.

\section{Risks}
\begin{itemize}
 \item Cars can be hacked
 \item Loss of driving-related jobs
 \item Moral Issues
\end{itemize}

\section{Obstacles}
\begin{itemize}
 \item Software reliability
 \item Autonomous cars rely on maps
 \item Inter-Car-Communication required
\end{itemize}

\section{Opportunities}
\begin{itemize}
 \item Reduction in traffic collisions
    \subitem 90\% less car accidents
    \subitem 190 billion US\$ savings in the United States
 \item Driver is not required
 \item Higher speed limits possible
 \item Higher fuel efficiency
\end{itemize}

\section{References}
\begin{itemize}
 \item{https://en.wikipedia.org/wiki/Autonomous\_car}
 \item{https://en.wikipedia.org/wiki/History\_of\_autonomous\_cars}
 \item{https://waymo.com}
 \item{http://lab.hakim.se/reveal-js/}
\end{itemize}

\end{document}
